### 2008-12-18 talk/ecoop2009/intro.tex
some notes about what the high-level overview should contain

\cfbolz{we should cite the dyla paper somewhere here}

PyPy's idea is to automatize the generation of JIT compilers in order
to reduce to a minimum the effort required to get a fast implementation of a
dynamic language; all you have to do is to write a high level specification of
the language (by writing an interpreter), and putting it through PyPy's
translation toolchain. The automatic generation of JIT compilers is done with
the help of partial evaluation techniques.

@@

The \emph{PyPy} project\footnote{\texttt{http://codespeak.net/pypy/dist/pypy/doc/home.html}}
\cite{RigoPedroni06} was initially conceived to develop an implementation of Python which
could be easily portable and extensible without renouncing efficiency.
To achieve these aims, the PyPy implementation is based on a highly
modular design which allows high-level aspects
to be separated from lower-level implementation details.
The abstract semantics of Python is defined by an interpreter written
in a high-level language, called RPython \cite{AACM-DLS07}, which is in fact a subset of
Python where some dynamic features have been sacrificed to allow an
efficient translation of the interpreter to low-level code.

@@

Another interesting feature of PyPy
is that just-in-time compilers can be semi-automatically generated from the
interpreter source.

XXX list contributions clearly

>>>>

\cfbolz{we should cite the dyla paper somewhere here. also, we generally need
more references}

PyPy's approach is to automatize the generation of JIT compilers in order
to reduce to a minimum the effort required to get a fast implementation of a
dynamic language; all you have to do is to write a high level specification of
the language (by writing an interpreter), and putting it through PyPy's
translation toolchain. The automatic generation of JIT compilers is done with
the help of partial evaluation techniques.

The contributions of this paper are \emph{promotion}, a generalization of
polymorphic inline caches that make partial evaluation practical for dynamic
languages and trying out the idea of JIT-layering XXX.

@@

The \emph{PyPy} project\footnote{\texttt{http://codespeak.net/pypy/}}
\cite{RigoPedroni06} was initially conceived to develop an implementation of Python which
could be easily portable and extensible without renouncing efficiency.
To achieve these aims, the PyPy implementation is based on a highly
modular design which allows high-level aspects
to be separated from lower-level implementation details.
The abstract semantics of Python is defined by an interpreter written
in a high-level language, called RPython \cite{AACM-DLS07}, which is in fact a subset of
Python where some dynamic features have been sacrificed to allow an
efficient translation of the interpreter to low-level code.

@@

- write an interpreter
- add some hints to the interpreter

translation time:
- start the translation process, flow graphs
- run a binding-time analysis using the hints, to figure out ...
- turn the flow graphs into rainbow bytecode
- turn the flow graphs of the rainbow interpreter and the original flow graphs
into .NET code

runtime:
when the interpreter is started and a function should be interpreted:
 - the generated JIT starts compiling the function 
 - it produces .NET bytecode until it does not have enough information to
 continue. then it stops the compilation and puts a callback into the compiler
 into the generated bytecode.
 - at this point the .NET bytecode that is produced so far is executed.
 - when the callback into the compiler is hit, execution stops and compilation
 starts again
 - afterwards execution continues after the callback (running the code that was
 newly produced)
